\documentclass{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola} % or any other font package you like
\usepackage{titlesec}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=NavyBlue,
}


\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname:\quad
  {\youremail}}

\newcommand{\soptitle}{Statement of Purpose}
\newcommand{\yourname}{Uzmar G\'omez}
\newcommand{\youremail}{uzmar.gomez@ciencias.unam.mx}
\newcommand{\yourweb}{https://uzmargomez.github.io/}

\newcommand{\statement}[1]{\par\medskip
  \underline{{\textbf{#1:}}}\space
}

\titleformat{\section}{\large\itshape}{\thesection}{1em}{}

\renewcommand{\bibsection}{\section*{Bibliography}}

\begin{document}
\spacing{1.5}
\begin{center}\LARGE\soptitle\\
\large of \yourname\ (UCD, MSc Computer Science (Negotiated Learning). September 2021 intake)
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\bigskip

Here I expose the reasons I have to get into the MCS Computer Science (Negotiated Learning).

First, I want to point out I knew about the "Conversion" program. However, by reading through the availability of modules, I strongly believe I have the experience and the knowledge required to succeed on the Negotiated Learning track. As you can see in my curriculum,  I have one year of experience as a Data Scientist. I know that perhaps this is not as much as some of the other students looking for a place, but I have shown my employers that I can be as good or even better than others who have more knowledge in this area than I do. I have studied and prepared a lot, managing to learn how to deliver production-level code in C ++ and Python on my own, I know about machine learning (I am currently creating a model to predict and prevent a customer from leaving Rackspace), containers and orchestration, and I have started to gain more experience with cloud services, in particular GCP, using tools like BigQuery, Airflow, Data Fusion, etc. As you can see, I am committed to learning as much as I can.

I also have experience in academy and research, I've been a teacher assistant of subjects such as computer science (directed to physics students), numerical relativity, and mathematics. To get my Physics degree, I made a \href{http://oreon.dgbiblio.unam.mx/F/YF3LAD8UIUFR2XRPDE3H6JM2MI44M8RY8QX1RH7K429163KKEV-19694?func=find-b&request=uzmar&find_code=WRD&adjacent=N&local_base=TES01&x=65&y=13&filter_code_2=WYR&filter_request_2=&filter_code_3=WYR&filter_request_3=}{thesis} of a finite difference method to solve and advective-kind equation called the Relativistic Vlasov Equation, on a background Schwarzschild metric. This work was made under \href{https://sigi.nucleares.unam.mx/sgiicn/people/user/view/id/8}{Dr. Alcubierre}'s guidance, at the \href{https://www.unam.mx/}{National Autonomous University of Mexico (UNAM)}.

To be clear, I do not want to pursue a Master's Degree to get a job, I have one and I am really interested in what I'm doing and I'm learning a lot, but I want to learn more, and upon seeing the module themes, I think UCD offers a really interesting variety of courses. For instance, I am most interested in the modules on the "Prediction and Learning with Data" theme (maybe because it is the one I'm most familiar with), but having the opportunity to attend courses on the "Artificial Intelligence and Cognitive Science", "Mathematics and Statistics" or "Software Engineering" sets, is something that really excites me about this program.

To be completely honest, I am debating if I would prefer to enter the industry again or pursue a PhD after the successful completion of the MSc. I have always been attracted to the academic environment, doing research and study different and new ideas, while sharing these ideas with students and learning from both teachers and fellow students and teammates, while working alongside top researches on the field. On the other side, I am sure that having an MSc Degree from UCD will give me the possibility to work on a top technology company in Dublin, which is a great opportunity. To be able to pursue either one of those paths is simply very attractive to me.

I hope I have been able to transmit my interest and my excitement, and I look forward to hearing about the decision regarding my acceptance. Please be sure that, if you accept me, I will do my best to succeed and learn all I can from this program and honour this great university.

\end{document}